### 2015-01-16 src/analysis.Rnw
update

\begin{figure*}
<<mutanttest,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, ncovering > 0)
d.db <- subset(allmutants.db, nkilling > 0)
m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling

>>>>

\begin{figure*}
<<mutanttest,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, ncovering > 0)
d.db <- subset(allmutants.db, nkilling > 0)
#m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
m.db$covering <- m.db$tstcovering * 100.0 / m.db$ntests
#d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling
d.db$killing <- d.db$tstkilling * 100.0 / d.db$ntests
